\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{listings}
\lstset{breaklines=true}
\usepackage{url}
\usepackage{dirtree}
\graphicspath{ {images/} }
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}


\begin{document}

\title{Truck Platooning System\\
{\footnotesize Formation of truck platoon}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Sheikh Muhammad Adib Bin Sh Abu Bakar}
\IEEEauthorblockA{\textit{Fachhochschule Dortmund} \\
\textit{ME. Embedded Systems Engineering}\\
sheikh.binshabubakar001@stud.fh-dortmund.de}

\and
\IEEEauthorblockN{2\textsuperscript{nd} Luis Fernando Rodriguez Gutierrez}
\IEEEauthorblockA{\textit{Fachhochschule Dortmund} \\
\textit{ME. Embedded Systems Engineering}\\
luis.rodriguez001@stud.fh-dortmund.de}

\and
\IEEEauthorblockN{3\textsuperscript{rd} Aditya Kumar}
\IEEEauthorblockA{\textit{Fachhochschule Dortmund} \\
\textit{ME. Embedded Systems Engineering}\\
aditya.kumar001@stud.fh.dortmund.de}

\and
\IEEEauthorblockN{4\textsuperscript{th} Leander Hackmann}
\IEEEauthorblockA{\textit{Fachhochschule Dortmund} \\
\textit{ME. Embedded Systems Engineering}\\
leander.hackmann001@stud.fh-dortmund.de}
\and
\IEEEauthorblockN{5\textsuperscript{th} Mykyta Konakh}
\IEEEauthorblockA{\textit{Fachhochschule Dortmund} \\
\textit{ME. Embedded Systems Engineering}\\
mykyta.konakh001@stud.fh-dortmund.de}
}

\maketitle



\input{section/01abstract}
\input{section/02introduction}
\input{section/03SystemAnalysis}
\input{section/04DesignAndImplementation:system}
\input{section/05DesignAndImplementation:truck}
\input{section/06DesignAndImplementation:communication}
\input{section/07VerificationAndValidation}
\input{section/08OutlookAndSummary}
\begin{thebibliography}{00}
\bibitem{b1} Hwang, Kai, Jack Dongarra, and Geoffrey C. Fox. Distributed and cloud computing: from parallel processing to the internet of things. Morgan kaufmann, 2013.
\bibitem{b2} Janssen, G. R., et al. "Truck platooning: Driving the future of transportation." (2015).  
\bibitem{b3}
@misc{rapp2024,
    title={Truck Platooning Image},
    author={Rapp.ch},
    howpublished={\url{https://www.rapp.ch/sites/default/files/styles/21by9_large/public/uploads/2018-10/rt-stories-truck-platooning-00_ohne_copyright.jpg?itok=3ugNaHXh}},
    year={2024}
}
\end{thebibliography}


\input{section/09GitHub}
%\input{section/10Contributors}
\input{section/11Affidavit}

\end{document}
